Mg Depleted and K Enriched Stars from LAMOST Spectral Data

### 2018-01-12 article/ms.tex
added tables minus abundances

\usepackage{tabularx}

@@

\usepackage{tikz}
\usepackage{hyperref}

\usepackage{color}
\newcommand{\todo}[1]{\textcolor{red}{#1}}

@@

The data set of \LamostGiants\ \lamost\ giants was prepared by \citet{ho2017} for use with the supervised machine learning code \tc. The \lamost\ data was shifted to rest frame and continuum-normalised \todo{double check with andy. I could have sworn she specifically said that it WASNT continuum normalised...} before it was resampled to a common uniform wavelength grid between 3905\,\AA\ and 9000\,\AA. \tc\ was used to infer $\teff$, $\logg$, [Fe/H], and [$\alpha$/Fe] using 9,952 stars in common between \lamost\ and the higher spectral resolution \apogee\ survey through the use of a data-driven spectral model. For details regarding the preparatory work, model generation, and label transfer between the \apogee\ and \lamost\ surveys, the reader is directed to \citet{ho2017}.

@@

\section{Some extra material}

If you want to present additional material which would interrupt the flow of the main paper,
it can be placed in an Appendix which appears after the list of references.

>>>>

\usepackage{verbatim}
\usepackage{tabularx}

@@

\usepackage{tikz}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{color}
\newcommand{\todo}[1]{\textcolor{red}{#1}}

@@

The data set of \LamostGiants\ \lamost\ giants was prepared by \citet{ho2017} for use with the supervised machine learning code \tc. The \lamost\ data was shifted to rest frame and pseudo-continuum-normalised \ before it was resampled to a common uniform wavelength grid between 3905\,\AA\ and 9000\,\AA. \tc\ was used to infer $\teff$, $\logg$, [Fe/H], and [$\alpha$/Fe] using 9,952 stars in common between \lamost\ and the higher spectral resolution \apogee\ survey through the use of a data-driven spectral model. For details regarding the preparatory work, model generation, and label transfer between the \apogee\ and \lamost\ surveys, the reader is directed to \citet{ho2017}.

@@

\section{Some extra material}
\begin{table}
\centering
\begin{tabular}{llllllllll}
\hline
\textbf{2MASSID} & \textbf{RA} & \textbf{DEC} & \textbf{S/N} & \textbf{Vr (km/s)} & \textbf{Teff} & \textbf{Logg} & \textbf{[Fe/H]} & \textbf{[Alpha/Fe]} & {$\boldsymbol \chi^\textbf{2}$} \\ \hline
J060142.80+132321.4 & 90.43 & 13.39 & 45 & 33.28 & 4858 & 2.57 & -0.30 & 0.10 & 0.24 \\ \hline
J075043.12+204658.0 & 117.68 & 20.78 & 47 & 52.46 & 4795 & 2.53 & -0.47 & 0.06 & 0.40 \\ \hline
J032450.35+352401.8 & 51.21 & 35.40 & 143 & 95.63 & 4908 & 3.33 & -0.27 & 0.19 & 0.70 \\ \hline
J214721.25+023958.7 & 326.84 & 2.67 & 104 & -63.83 & 4649 & 2.22 & -0.68 & 0.26 & 0.81 \\ \hline
J040340.38+563902.4 & 60.92 & 56.65 & 30 & 39.87 & 4459 & 2.05 & -0.46 & 0.01 & 0.61 \\ \hline
J035455.85+594730.3 & 58.73 & 59.79 & 57 & -40.17 & 4956 & 2.81 & 0.08 & 0.04 & 0.56 \\ \hline
J035928.29+595932.8 & 59.87 & 59.99 & 35 & -38.07 & 4808 & 2.44 & -0.53 & 0.16 & 0.32 \\ \hline
J034458.82+592955.1 & 56.25 & 59.50 & 53 & -32.68 & 4811 & 2.66 & 0.06 & 0.10 & 0.64 \\ \hline
J220657.78+232138.3 & 331.74 & 23.36 & 50 & -27.58 & 4842 & 3.34 & -0.40 & 0.10 & 0.23 \\ \hline
J061323.14+325543.0 & 93.35 & 32.93 & 39 & -25.78 & 4861 & 2.51 & -0.40 & 0.16 & 0.42 \\ \hline
J005649.98+391722.9 & 14.21 & 39.29 & 41 & -46.77 & 4578 & 2.67 & 0.31 & 0.10 & 0.44 \\ \hline
J002619.36+565612.1 & 6.58 & 56.94 & 31 & -39.57 & 4205 & 1.49 & 0.22 & 0.06 & 0.76 \\ \hline
J040817.31+463252.5 & 62.07 & 46.55 & 92 & -1.80 & 5019 & 2.68 & -0.09 & 0.05 & 0.98 \\ \hline
J072156.18+225405.3 & 110.48 & 22.90 & 101 & -46.77 & 4840 & 2.54 & -0.33 & 0.17 & 0.69 \\ \hline
J040634.97+411354.9 & 61.65 & 41.23 & 45 & -35.38 & 4770 & 2.67 & -0.26 & 0.07 & 0.51 \\ \hline
J041608.62+433504.7 & 64.04 & 43.58 & 30 & -20.09 & 4967 & 2.90 & -0.17 & 0.04 & 0.33 \\ \hline
J013039.08+404843.8 & 22.66 & 40.81 & 71 & -80.34 & 4355 & 2.01 & -0.09 & 0.14 & 0.93 \\ \hline
J052924.25+494319.7 & 82.35 & 49.72 & 94 & -22.48 & 5087 & 3.12 & -0.35 & 0.11 & 0.70 \\ \hline
J061427.58+331544.3 & 93.61 & 33.26 & 51 & 3.30 & 4468 & 1.87 & -0.41 & 0.11 & 0.67 \\ \hline
J062128.63+343545.8 & 95.37 & 34.60 & 39 & 33.28 & 4831 & 2.58 & -0.23 & 0.08 & 0.27 \\ \hline
J030101.42+560042.3 & 45.26 & 56.01 & 88 & -39.27 & 4878 & 2.53 & -0.32 & 0.09 & 0.67 \\ \hline
J120032.60+024438.2 & 180.14 & 2.74 & 97 & 166.98 & 4633 & 2.33 & -0.93 & 0.26 & 0.89 \\ \hline
J163910.01+100545.3 & 249.79 & 10.10 & 39 & 123.81 & 4663 & 2.46 & -0.58 & 0.03 & 0.61 \\ \hline
\end{tabular}
\caption{My caption}
\label{my-label}
\end{table}

\newpage
\begin{comment}
\begin{table}[H]
\centering
\begin{tabular}{llllllllll}
\hline
\textbf{2MASSID} & \textbf{RA} & \textbf{DEC} & \textbf{S/N} & \textbf{Radial\_Velocity\_(km/s)} & \textbf{Teff} & \textbf{Logg} & \textbf{{[}Fe/H{]}} & \textbf{{[}Alpha/Fe{]}} & \textbf{$\chi^2$} \\ \hline
J234942.32+300654.0 & 357.43 & 30.11 & 20 & -195.46 & 4004 & 1.12 & -0.58 & 0.23 & 2.73 \\ \hline
J065334.23+131639.7 & 103.39 & 13.28 & 7 & 179.88 & 4896 & 2.61 & -0.71 & 0.02 & 0.18 \\ \hline
J112309.75+261255.9 & 170.79 & 26.22 & 3 & 113.02 & 4273 & 1.13 & -1.35 & 0.17 & 0.09 \\ \hline
J111651.71+253038.5 & 169.22 & 25.51 & 6 & 102.83 & 4658 & 2.90 & -0.50 & 0.02 & 0.08 \\ \hline
J045424.86+534628.5 & 73.60 & 53.77 & 6 & -36.57 & 4451 & 1.81 & -0.19 & 0.07 & 0.37 \\ \hline
J065857.80+081714.8 & 104.74 & 8.29 & 12 & 26.68 & 5070 & 3.30 & -0.61 & 0.10 & 0.18 \\ \hline
J045544.93+490023.3 & 73.94 & 49.01 & 6 & -38.07 & 4717 & 2.55 & -0.34 & 0.11 & 0.11 \\ \hline
J040739.62+423724.4 & 61.92 & 42.62 & 9 & -37.77 & 4075 & 1.54 & -0.32 & 0.08 & 0.28 \\ \hline
J043121.48+414757.2 & 67.84 & 41.80 & 8 & -12.59 & 4537 & 2.07 & -0.09 & 0.03 & 0.13 \\ \hline
J041900.21+422223.9 & 64.75 & 42.37 & 12 & -34.18 & 4263 & 1.77 & -0.55 & 0.09 & 0.28 \\ \hline
J041209.44+411801.0 & 63.04 & 41.30 & 35 & -20.69 & 4767 & 2.24 & -0.26 & 0.12 & 0.91 \\ \hline
J063648.82+130723.3 & 99.20 & 13.12 & 8 & 85.74 & 4925 & 2.93 & -0.57 & -0.03 & 0.19 \\ \hline
J070524.04+120351.0 & 106.35 & 12.06 & 19 & 60.26 & 4754 & 2.64 & -0.56 & -0.02 & 0.24 \\ \hline
J063501.25+134744.6 & 98.76 & 13.80 & 7 & 47.67 & 4612 & 2.33 & -0.40 & 0.01 & 0.19 \\ \hline
J053942.83+383727.8 & 84.93 & 38.62 & 18 & -85.74 & 4979 & 2.26 & -0.66 & 0.23 & 0.27 \\ \hline
J053123.26+421952.0 & 82.85 & 42.33 & 8 & 41.07 & 4785 & 2.59 & -0.26 & 0.01 & 0.26 \\ \hline
J052643.65+354130.3 & 81.68 & 35.69 & 9 & -18.89 & 4914 & 2.73 & -0.09 & 0.03 & 0.28 \\ \hline
J064618.82+050545.8 & 101.58 & 5.10 & 9 & 85.74 & 4772 & 2.66 & -0.49 & -0.01 & 0.28 \\ \hline
J063719.82+185602.6 & 99.33 & 18.93 & 5 & 15.29 & 5075 & 2.94 & -0.12 & 0.03 & 0.10 \\ \hline
J072912.52+073436.9 & 112.30 & 7.58 & 9 & 117.52 & 4835 & 3.18 & -0.44 & 0.33 & 0.34 \\ \hline
J193217.91+374505.6 & 293.07 & 37.75 & 28 & -70.15 & 4982 & 2.62 & -0.48 & 0.33 & 0.55 \\ \hline
J192937.24+390211.0 & 292.41 & 39.04 & 6 & -52.16 & 4819 & 3.00 & 0.37 & 0.12 & 0.21 \\ \hline
J010305.95+043445.9 & 15.77 & 4.58 & 90 & 20.69 & 4646 & 2.72 & 0.10 & 0.05 & 1.17 \\ \hline
J235454.61+110356.9 & 358.73 & 11.07 & 12 & -109.72 & 4794 & 3.07 & -0.16 & 0.30 & 0.21 \\ \hline
J000908.89+124821.9 & 2.29 & 12.81 & 10 & -78.55 & 4892 & 2.82 & -0.12 & 0.33 & 0.19 \\ \hline
J220115.66-001432.2 & 330.32 & -0.24 & 47 & 38.37 & 4925 & 3.30 & 0.06 & 0.23 & 0.32 \\ \hline
J064430.22+341606.3 & 101.13 & 34.27 & 9 & -40.17 & 4809 & 3.26 & 0.36 & 0.19 & 0.31 \\ \hline
J002907.61+354701.0 & 7.28 & 35.78 & 15 & -82.74 & 5116 & 3.56 & 0.24 & 0.17 & 0.18 \\ \hline
J033714.25+403015.1 & 54.31 & 40.50 & 34 & -119.32 & 4674 & 2.33 & 0.32 & 0.22 & 0.86 \\ \hline
J074807.22+261514.2 & 117.03 & 26.25 & 16 & -32.98 & 4846 & 2.69 & -0.23 & 0.05 & 0.16 \\ \hline
J032423.46+425429.6 & 51.10 & 42.91 & 23 & -56.74 & 4649 & 2.63 & -0.11 & -0.01 & 0.34 \\ \hline
J055043.44+162021.2 & 87.68 & 16.34 & 24 & 83.64 & 4587 & 2.49 & 0.21 & 0.07 & 0.28 \\ \hline
J055227.43+181628.0 & 88.11 & 18.27 & 28 & 8.09 & 5388 & 3.80 & -0.17 & 0.05 & 0.43 \\ \hline
J055935.08+150252.1 & 89.90 & 15.05 & 23 & 90.84 & 4487 & 2.15 & -0.68 & 0.01 & 4.35 \\ \hline
J063113.14+015900.3 & 97.80 & 1.98 & 14 & 78.55 & 4879 & 2.34 & -0.13 & 0.01 & 0.56 \\ \hline
J111550.58+104203.9 & 168.96 & 10.70 & 9 & 114.82 & 4519 & 1.72 & -1.41 & 0.32 & 0.17 \\ \hline
J111022.65+171251.0 & 167.59 & 17.21 & 12 & 247.33 & 4524 & 1.92 & -1.30 & 0.13 & 0.30 \\ \hline
J100054.32+185535.5 & 150.23 & 18.93 & 17 & 149.00 & 4373 & 2.30 & 0.01 & 0.01 & 0.39 \\ \hline
J055908.72+210037.7 & 89.79 & 21.01 & 6 & 55.76 & 4325 & 1.99 & -0.10 & -0.03 & 0.75 \\ \hline
J055704.30+215000.1 & 89.27 & 21.83 & 9 & 49.77 & 4691 & 2.94 & 0.37 & 0.00 & 0.30 \\ \hline
J104800.91+424311.0 & 162.00 & 42.72 & 6 & 163.99 & 5050 & 2.75 & -1.29 & 0.12 & 0.18 \\ \hline
J075129.58+024136.9 & 117.87 & 2.69 & 18 & 128.61 & 4741 & 2.39 & -0.61 & 0.05 & 0.28 \\ \hline
J064132.46+580400.9 & 100.39 & 58.07 & 24 & -11.69 & 5285 & 3.74 & -0.06 & 0.07 & 0.36 \\ \hline
J063908.57+381728.0 & 99.79 & 38.29 & 5 & 25.78 & 4853 & 2.73 & -0.52 & 0.02 & 0.17 \\ \hline
J102104.26+105617.4 & 155.27 & 10.94 & 17 & 171.48 & 4526 & 1.88 & -1.09 & 0.07 & 0.28 \\ \hline
J061228.04-040304.1 & 93.12 & -4.05 & 16 & -1.50 & 4928 & 3.24 & -0.56 & 0.09 & 0.19 \\ \hline
J061144.17-040845.1 & 92.93 & -4.15 & 23 & 84.54 & 4709 & 2.77 & -0.42 & -0.00 & 0.24 \\ \hline
J074848.57+210655.5 & 117.20 & 21.12 & 9 & 101.33 & 4447 & 2.25 & -0.52 & 0.04 & 0.11 \\ \hline
J092124.00+204559.5 & 140.35 & 20.77 & 12 & 125.31 & 4570 & 2.28 & -0.71 & 0.06 & 0.31 \\ \hline
J074146.65+145330.5 & 115.44 & 14.89 & 6 & 105.53 & 4701 & 2.00 & -0.71 & 0.04 & 0.18 \\ \hline
J073641.12+164710.6 & 114.17 & 16.79 & 6 & 90.84 & 4621 & 2.17 & -0.77 & 0.01 & 0.26 \\ \hline
J175211.80+273546.6 & 268.05 & 27.60 & 7 & -33.58 & 5489 & 3.71 & -0.03 & 0.14 & 0.15 \\ \hline
J194028.76+504047.6 & 295.12 & 50.68 & 22 & -61.76 & 4352 & 1.94 & -0.17 & 0.23 & 0.35 \\ \hline
J213914.06+025536.2 & 324.81 & 2.93 & 29 & 57.78 & 4488 & 2.40 & -0.37 & 0.05 & 0.46 \\ \hline
J011949.36+063411.4 & 19.96 & 6.57 & 479 & -28.18 & 4820 & 2.61 & -0.29 & 0.09 & 2.38 \\ \hline
J041055.45+570542.6 & 62.73 & 57.10 & 16 & -32.38 & 4141 & 1.66 & -0.23 & 0.07 & 0.47 \\ \hline
J035840.66+574934.5 & 59.67 & 57.83 & 17 & -56.06 & 4693 & 2.02 & -0.28 & 0.14 & 0.46 \\ \hline
J034552.01+595739.3 & 56.47 & 59.96 & 17 & -48.57 & 4627 & 2.07 & -0.38 & 0.16 & 0.41 \\ \hline
J193130.64+432204.2 & 292.88 & 43.37 & 16 & -92.64 & 4934 & 3.08 & -0.16 & 0.30 & 0.26 \\ \hline
J042753.62+365550.6 & 66.97 & 36.93 & 8 & -30.08 & 5249 & 2.91 & -0.21 & 0.18 & 0.30 \\ \hline
J061808.85+313338.2 & 94.54 & 31.56 & 12 & 42.57 & 4970 & 3.03 & -0.15 & 0.10 & 0.55 \\ \hline
J050740.59+492955.0 & 76.92 & 49.50 & 15 & 18.29 & 3879 & 0.96 & -0.72 & 0.06 & 0.54 \\ \hline
J050606.74+494925.0 & 76.53 & 49.82 & 25 & -28.78 & 4857 & 2.50 & -0.25 & 0.12 & 0.34 \\ \hline
J050551.93+493726.0 & 76.47 & 49.62 & 15 & -18.59 & 4961 & 2.85 & -0.47 & 0.07 & 0.27 \\ \hline
J051046.05+523848.3 & 77.69 & 52.65 & 47 & -46.17 & 4697 & 2.61 & -0.34 & 0.26 & 1.03 \\ \hline
J041321.95+520135.7 & 63.34 & 52.03 & 19 & -51.35 & 4694 & 2.48 & -0.05 & 0.05 & 0.50 \\ \hline
J065356.76+344513.1 & 103.49 & 34.75 & 21 & -23.38 & 4533 & 2.46 & -0.00 & 0.15 & 0.28 \\ \hline
J003451.10+424543.0 & 8.71 & 42.76 & 15 & -79.15 & 4460 & 2.10 & -0.56 & 0.24 & 0.31 \\ \hline
J040034.51+472103.8 & 60.14 & 47.35 & 18 & -55.82 & 4708 & 2.39 & -0.01 & 0.10 & 0.65 \\ \hline
J041304.73+470013.8 & 63.27 & 47.00 & 17 & 19.19 & 4290 & 1.79 & -0.37 & 0.03 & 0.79 \\ \hline
J035633.86+463749.2 & 59.14 & 46.63 & 17 & -54.93 & 4753 & 2.37 & -0.05 & 0.12 & 0.34 \\ \hline
J053627.38+581132.8 & 84.11 & 58.19 & 28 & -32.94 & 4457 & 2.52 & 0.28 & 0.05 & 0.49 \\ \hline
J052516.26+585912.5 & 81.32 & 58.99 & 19 & -75.07 & 4023 & 1.50 & -0.22 & 0.05 & 0.51 \\ \hline
J034826.25+350123.4 & 57.11 & 35.02 & 100 & -47.97 & 4710 & 2.89 & 0.04 & 0.38 & 4.72 \\ \hline
J035652.48+325937.2 & 59.22 & 32.99 & 24 & -20.99 & 4038 & 1.38 & -0.31 & 0.08 & 0.55 \\ \hline
J035345.63+340429.3 & 58.44 & 34.07 & 15 & -34.48 & 4830 & 3.23 & -0.56 & 0.06 & 0.14 \\ \hline
J042245.32+430359.8 & 65.69 & 43.07 & 16 & -35.08 & 4967 & 2.92 & -0.13 & 0.03 & 0.20 \\ \hline
J042241.36+414255.6 & 65.67 & 41.72 & 15 & -92.76 & 4975 & 3.32 & -0.66 & 0.02 & 0.27 \\ \hline
J053148.24+225045.6 & 82.95 & 22.85 & 15 & 11.69 & 3982 & 0.71 & -0.84 & 0.08 & 0.63 \\ \hline
J120844.42-012151.8 & 182.19 & -1.36 & 18 & 143.30 & 4783 & 2.28 & -0.84 & 0.28 & 0.48 \\ \hline
J091825.49+172114.5 & 139.61 & 17.35 & 11 & 232.04 & 4898 & 2.71 & -1.19 & 0.29 & 0.14 \\ \hline
J123413.43+160353.7 & 188.56 & 16.06 & 10 & 316.88 & 4734 & 2.63 & -0.99 & 0.03 & 0.17 \\ \hline
J054656.93+442800.0 & 86.74 & 44.47 & 17 & -41.37 & 4758 & 2.51 & -0.27 & 0.09 & 0.15 \\ \hline
J053423.46+460026.9 & 83.60 & 46.01 & 21 & -40.77 & 4893 & 2.73 & -0.18 & 0.10 & 0.26 \\ \hline
J052814.58+511912.4 & 82.06 & 51.32 & 16 & -64.76 & 4344 & 1.95 & -0.06 & 0.10 & 0.51 \\ \hline
J044403.36+543203.6 & 71.01 & 54.53 & 19 & -71.05 & 4625 & 1.91 & 0.25 & 0.07 & 1.42 \\ \hline
J043503.82+552514.6 & 68.77 & 55.42 & 19 & 9.59 & 4704 & 2.48 & -0.11 & 0.04 & 0.60 \\ \hline
J043418.64+535250.2 & 68.58 & 53.88 & 17 & -141.15 & 4204 & 1.44 & -0.64 & 0.19 & 0.76 \\ \hline
J070937.38+201517.2 & 107.41 & 20.25 & 9 & 148.10 & 3770 & 0.19 & -1.24 & 0.04 & 0.46 \\ \hline
J064032.35+335207.5 & 100.13 & 33.87 & 8 & -34.48 & 4717 & 2.28 & -0.44 & 0.24 & 0.24 \\ \hline
\end{tabular}
\caption{Remaining candidates}
\label{Resttab}
\end{table}
\end{comment}
